### 2014-05-01 ApTranscriptome_TR.Rmd
Updated script to use full Trinity assembly including contaminant reads. Confirmed previous Sailfish mapping results.

    sailfish index -t Trinity_cap3_uclust_clean.fasta -o sailfish-index -k 20 -p 4

@@

    mkdir sailfish-expression

@@

```{r sailfish, eval=TRUE, echo=TRUE, cache=TRUE}
# directory containing trimmed reads
readdir <- "data/ind_files/" 
# sailfish index directory
sfindex <- "results/trinity-full/sailfish-index"
# sailfish expression directory
sfexpressionroot <- "results/trinity-full/sailfish-expression/"

@@

```{r padjust}
RxNpval$padj <- p.adjust(RxNpval$pval, method = "fdr")
# Plot FDR values against initial pvalues
par(mfrow = c(2,1))
hist(RxNpval$pval)
hist(RxNpval$padj)

>>>>

    sailfish index -t Trinity_cap3_uclust_clean.fasta -o sailfish-index-Trinity_cap3_uclust -k 20 -p 4

@@

    mkdir sailfish-expression-Trinity-cap3-uclust

@@

```{r sailfish, eval=TRUE, echo=TRUE, cache=TRUE}
# directory containing trimmed reads
readdir <- "data/ind_files/" 
# sailfish index directory
sfindex <- "results/trinity-full/sailfish-index-Trinity_cap3_uclust"
# sailfish expression directory
sfexpressionroot <- "results/trinity-full/sailfish-expression-Trinity-cap3-uclust/"

@@

```{r padjust}
RxNpval$padj <- p.adjust(RxNpval$pval, method = "fdr")
# Plot FDR values against initial pvalues
png(file=paste(resultsdir, "pval_hist.png"))
par(mfrow = c(2,1))
hist(RxNpval$pval)
hist(RxNpval$padj)
dev.off()
